Failure Behaviour Analysis of Automated Pond Oxygen Management System

### 2015-02-19 IFIP FTA/manuscript.tex
some edit

\author{Sohag Kabir\inst{1}\and Youcef Gheraibia\inst{2}\and Tanzima Azad\inst{3}}
\institute{Department of Computer Science, University of Hull, Hull, UK\and Department of Computer Science, Badji Mokhtar-Annaba University, Annaba, Algeria\and Department of Computer Science and Engineering, Bangladesh University of Enegineerinag \& Technology, Bangladesh\\
\email{s.kabir@hull.ac.uk, youcef.gheraibia@gmail.com, azad.tanzima@dbbl.com.bd}
}
\maketitle

\begin{abstract}
%\boldmath
Reliability of safety-critical systems are a prime concern of the modern society due to the growing dependence on those systems. Safety of systems is a fundamental requirement for system reliability. Fault tree analysis (FTA) is well-established, powerful, and widely used tool for evaluating system reliability. Fault trees provide a graphical and logical framework for analysing the dependability of systems. They have been successfully employed in studying reliability of a variety of real-world systems. In aquaculture, the volume of oxygen contained in water is considered as a critical parameter for the health and well-being of fishes. If oxygen levels drop below 4 mg/L then fishes may stop feeding, stressed and begin to die. Automated Pond Oxygen Management System is a critical component in aquaculture to maintain the proper oxygen level in water. In summer months, when oxygen level starts dropping due to increased temperature, then Automated Pond Oxygen Management System can balance the oxygen level in water by generating oxygen artificially. Therefore, the failure of this system may result in a disastrous outcome. In this paper, we have used fault tree analysis to evaluate the reliability of a generic automated fault tolerant pond oxygen management system.
\end{abstract}

@@

FTA has been widely used in different areas to perform both qualitative and quantitative dependability analysis of the systems. Systems that have been analysed using FTA include but not limited to propulsion systems on spacecraft, braking systems in cars, Nuclear Power Plants, and so on. FTA has been used to analyse the reliability of the power system in  \cite{volkanovski2009,cepin2011assessment}, power supply system to railways in  \cite{Chen2007}, and cogeneration power plant in textile mill in \cite{Ramesh2011}.  Recently, fault tree analysis has been applied on Clinical workflows to ensure the safety of these high-risk workflows \cite{lamis2014} and it is also used to prevent wrong-side surgery to patients \cite{abecassis2015}. \textbf{The fault tree for pressure tank analysis has been proposed in [NASA Office of Safety and Mission Assurance].
Elctornics system has used the FTA to study the behaviour of electronics system. Authors in \cite{shu2006using} uses FTA on printed circuit board assembly and 
for assessment of power system reliability [Reliability Engineering  System Safety]. The biological system uses the FTA to analysis the failure of biomedical operation such as Analysis for Biological Invasions  \cite{hayes2002identifying}.} Different tools like HiP-HOPS\cite{Papadopoulos2012}, Reliability Workbench\cite{Isograph2014}  are available to perform fault tree analysis.

>>>>

\author{Sohag Kabir\inst{1}\and Youcef Gheraibia\inst{2}\and Tanzima Azad\inst{3}}
\institute{Department of Computer Science, University of Hull, Hull, UK\and Department of Computer Science and Mathematics,  Mohamed-Cherif Messaadia University, Souk Ahras, Algeria\and Department of Computer Science and Engineering, Bangladesh University of Enegineerinag \& Technology, Dhaka, Bangladesh\\
\email{s.kabir@hull.ac.uk, youcef.gheraibia@univ-soukahras.dz, azad.tanzima@dbbl.com.bd}
}
\maketitle

\begin{abstract}
%\boldmath
Dependability of safety-critical systems is a prime concern of the modern society due to the growing dependence on those systems. Safety of systems is a fundamental requirement for system reliability. Fault tree analysis (FTA) is well-established, powerful, and widely used tool for evaluating system safety. Fault trees provide a graphical and logical framework for analysing the dependability of systems. They have been successfully employed in studying failure behaviour of a variety of real-world systems. In aquaculture, the volume of oxygen contained in water is considered as a critical parameter for the health and well-being of fishes. If oxygen levels drop below 4 mg/L then fishes may stop feeding, stressed and begin to die. Automated Pond Oxygen Management System (APOMS) is a critical component in aquaculture to maintain the proper oxygen level in water. In summer months, when oxygen level starts dropping due to increased temperature, then the APOMS can balance the oxygen level in water by generating oxygen artificially. Therefore, the failure of this system may result in a disastrous outcome. In this paper, we have used fault tree analysis to evaluate the reliability of a generic automated fault tolerant pond oxygen management system.
\end{abstract}

@@

FTA has been widely used in different areas to perform both qualitative and quantitative dependability analysis of the systems. Systems that have been analysed using FTA include but not limited to propulsion systems on spacecraft, braking systems in cars, Nuclear Power Plants, and so on. Different tools like HiP-HOPS\cite{Papadopoulos2012}, Reliability Workbench\cite{Isograph2014}  are available to perform fault tree analysis. FTA has been used to analyse the reliability of the power system in  \cite{volkanovski2009,cepin2011assessment}, power supply system to railways in  \cite{Chen2007}, and cogeneration power plant in textile mill in \cite{Ramesh2011}.  Recently, fault tree analysis has been applied on Clinical workflows to ensure the safety of these high-risk workflows \cite{lamis2014} and it is also used to prevent wrong-side surgery to patients \cite{abecassis2015}. Authors in \cite{shu2006using} uses FTA to analyse the potential failure scenarios in the assembly process of the printed circuit board industries. In the biological domain, FTA is used to analyse the failure of biomedical operation such as analysis for biological invasions  \cite{hayes2002identifying}.
